An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-01-10 EconGrowth2.Rnw
createHistoricalLatticeGraph -> historicalPlot

<<Historical_Lattice_Graph, fig.pos="H", fig.width=maxWidth, fig.height=maxHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
createHistoricalLatticeGraph()
@

>>>>

<<Historical_Lattice_Graph, fig.pos="H", fig.width=maxWidth, fig.height=maxHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
historicalPlot()
@
